% Document class and font size
\documentclass[letterpaper, 9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\usepackage{xcolor}
\geometry{letterpaper, margin=0.75in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting

\usepackage{enumitem} % For itemized list formatting
\setlist[itemize]{noitemsep, topsep=0pt}

\usepackage{hyperref} % For hyperlinks

\usepackage{fontawesome}



% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing

% Typeset "C++"
\newcommand{\CPP}{C\nolinebreak\hspace{-.05em}\raisebox{.4ex}{\tiny\bf +}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\tiny\bf +}}

\begin{document}

% Disable page numbers
\pagestyle{empty}

% Header
\begin{center}
    \textbf{\Large ADEN CHEN} \\
    \href{tel:(872) 899-4015}{\faMobile\space (872) 899-4015}
    $|$
    \href{mailto:adenc@uchicago.edu}{\faAt\space adenc@uchicago.edu}
    $|$
    \hspace{.5pt}\href{https://adenchen27.github.io/}{\faGlobe\space Portfolio}
    % \href{https://www.linkedin.com/in/aden-chen-45a924221/}{\faLinkedinSquare \space LinkedIn}
    $|$
    \href{https://github.com/AdenChen27}{\faGithub\space Github}
    % $|$
\end{center}

% Education Section
\section*{EDUCATION}
\noindent
\textbf{The University of Chicago} \hfill Expected, June 2027 \\ 
\textit{Bachelor of Arts in Economics and Mathematics} \hfill \textit{Chicago, IL}
% \textbf{Relevent Coursework}
% \noindent
\begin{itemize}
    \item\textbf{GPA:} 3.950 
    % \item\textbf{Relevant Coursework:} Honors Calculus II, Systems Programming II, Multiscale Modeling of Biological Systems II, Introduction to Data Science, Approaches to Digital Humanities Using Python
    % \item\textbf{Others:} Oeconomica, International Collegiate Programming Contest (ICPC)
\end{itemize}

% Experience Section
\section*{RESEARCH}

\noindent
\textbf{Becker Friedman Institute Summer Internship Program: MiiE Lab} 
\hfill June 2024 -- August 2024 \\
\textit{Research Assistant} 
\begin{itemize}
  \item Supported Professor Adukia in her work to analyze images and texts in textbooks, children’s books, and yearbooks using computational methods.
  \item Crawled yearbook data from dynamic websites, and ran computer vision pipelines to estimate gender and race proportions in schools.
Ran various natural language processing algorithms on news articles, including emotion analysis, VAD analysis, log odds ratio with Dirichlet prior, name entity recognition, power and agency analysis, topic modeling, among others.
\end{itemize}

% \noindent
% \textbf{UChicago Mathematics Research Experience for Undergraduates (REU)} 
% \hfill June 2024 -- September 2024 \\
% \textit{Apprentice Researcher} 
% \begin{itemize}
%   \item Attend lectures covering a variety of topics in analysis and probability, such as random walks, the heat equation, and closed geodesics. 
%   \item Self-studied functional analysis, with a focus on ...
% \end{itemize}


\noindent
\textbf{Research Assistant under Professor Shaoda Wang and Professor Daniel Li Chen} 
\hfill April 2024 -- June 2024 \\
\textit{Research Assistant} 
\begin{itemize}
  \item Developed pipeline for crawling legal documents in court cases involving expert witness. Downloaded over 3M relevant documents and metadata for over 1.5M cases. 
\end{itemize}


\noindent
\textbf{Nationalism Sentiment during Covid-19 in China} 
\hfill February 2023 -- March 2023 \\
\textit{Research Assistant} 
\begin{itemize}
    \item Utilized Python to scrape blogs posted on Weibo from 2018 to 2022, focusing on topics related to the US, collecting data for sentiment analysis.
\end{itemize}

\noindent
\textbf{Gender Differences in Psychology}
[\href{https://drive.google.com/file/d/19cO9fOI9KPIAT2OV0WPENLVXvrM-A7fZ/view?usp=sharing}{\color{blue} \underline{PDF}}]
\hfill May 2022 -- June 2022 \\
\textit{Researcher} 
\begin{itemize}
    \item Investigated the gender differences in personality and career preferences. 
    \item Paper discussing both biological and social factors and the gender equality paradox won commendation in the John Locke Institute Global Essay Competition.
\end{itemize}

% \noindent
% \textbf{How Perceptions of Intelligence Influence Education} 
% [\href{https://drive.google.com/file/d/1lgQKk7_geC_NsAG5uHnPfWY3wKy38_-o/view?usp=sharing}{\color{blue} \underline{PDF}}]
% \hfill February 2022 -- March 2022 \\
% \textit{Researcher} 
% \begin{itemize}
%     \item Wrote a research paper on the interplay between students' implicit theory of intelligence and stereotype threats, classroom interventions that promote a harmful fixed mindset, and possible interventions to promote a growth mindset. 
% \end{itemize}

% \noindent
% \textbf{Short-Circuits in the Mind} \hfill  \\
% \textit{Researcher} \hfill May 2021 – June 2021
% \begin{itemize}
%     \item Researched and the dual process model and wrote paper analyzing the process of "doubt and investigation,” people's "common sense," and how the brain "short-circuits" itself. I then discussed how cults and fake news might utilize this feature of the brain and possible mitigative measures.
% \end{itemize}


% Leadership & Activities
\section*{LEADERSHIP \& ACTIVITIES}


\noindent
\textbf{Recognized Student Organization: Oeconomica} 
\hfill October 2023 -- Present \\
\textit{Member in the Econometrics Cohort} \hfill \textit{Chicago, IL}
\begin{itemize}
    \item Attend weekly lectures and faculty talks, learning about causal inference, linear regression, R, instrumental variable, \LaTeX, and acquiring insights into the latest faculty research.
\end{itemize}

\noindent
\textbf{International Collegiate Programming Contest (ICPC)} 
\hfill October 2023 -- Present \\
\textit{Member} \hfill \textit{Chicago, IL}
\begin{itemize}
    \item Actively participate in weekly training sessions for ICPC.
\end{itemize}


\noindent
\textbf{Popular Science Articles} 
\hfill January 2023 -- Present \\
\textit{Organizer \& Creator}
\begin{itemize}
    % \item Coordinated team of 15+ writers, researchers, and editors in the creation of content for a popular science blog.
    \item Wrote several articles on behavioral economics, touching on topics including expected utility theory and prospect theory, risk aversion and loss aversion, status quo bias, economic games, social preferences and altruism, competitiveness and the gender equality paradox, framing effect, and scarcity theory. 
    \item Created mathematical animations for economics concepts using Python and \href{https://www.manim.community/}{Manim}. [\href{https://github.com/AdenChen27/Econic}{\color{blue} \underline{GitHub}}].
\end{itemize}

% Programming Projects
% \section*{PROGRAMMING PROJECTS}

% \noindent
% \textbf{ESL Learning Website} 
% [\href{https://github.com/AdenChen27/Project_0}{\color{blue} \underline{GitHub}}]
% \hfill September 2021 -- June 2023  \\
% \textit{Developer}
% \begin{itemize}
%     \item Developed a Django-based website for interactive learning, integrating auto-generated quizzes for word comprehension. 
%     \item Recognized as a finalist in the Rise Global Challenge by Schmidt Futures and the Rhodes Trust.
% \end{itemize}

\noindent
\textbf{Online APA7 In-Text Citation Checker} 
[\href{https://github.com/AdenChen27/AdenChen27.github.io/tree/main/citation_checker}{\color{blue} \underline{GitHub}}]
\hfill June 2022 -- August 2022 \\
\textit{Developer} 
\begin{itemize}
    \item Designed and developed a \href{https://adenchen27.github.io/citation_checker/main.html}{\color{blue} \underline{webpage}} utilizing JavaScript and RegEx to check the format of APA7-styled in-text citations.
\end{itemize}

% \noindent
% \textbf{2048 Solver} 
% [\href{https://github.com/AdenChen27/2048_solver}{\color{blue} \underline{GitHub}}]
% \hfill January 2021 \\
% \textit{Developer} 
% \begin{itemize}
%     \item Wrote a program in \CPP \space that plays the game 2048 using Minimax algorithm and Alpha--Beta pruning. 
% \end{itemize}


%\noindent
%\textbf{ESL Tutoring Team} 
%\hfill  \\
%\textit{Organizer \& Tutor} \hfill January 2023 -- August 2023
%\begin{itemize}
%    \item Led team of 3 tutoring middle and high school students. Designed and delivered a total of 96 ESL classes to middle and high school students. Donated income to Project Hope.
%\end{itemize}

% \noindent
% \textbf{School Olympiad Team in Informatics} 
% \hfill  \\
% \textit{Team Member} \hfill September 2019--October 2022
% \begin{itemize}
%    \item Won multiple individual top prizes in China's National Olympiad in Informatics in Province (NOIP) and China Computer Foundation’s Certified Senior non-Pro contests, senior division (CSP-S).
% \end{itemize}

% \noindent
% \textbf{China Thinks Big Innovation and Research Competition} 
% \hfill  \\
% \textit{Team Member} \hfill October 2021 -- March 2022
% \begin{itemize}
%    \item Researched and addressed the psychological roots of gender gap in high school sports participation. 
%    \item Developed website for project using Python and Django. 
%    \item Created online showcase. Won national second award. 
   
% \end{itemize}

% Skills
\section*{SKILLS}
% \textbf{Languages:} Mandarin, English \\ 
% \textbf{Computing:} Proficient in Python and \CPP\@. Familiar with R, JavaScript, C, HTML/CSS, and \LaTeX.
\textbf{Programming:} Python, C/\CPP\@, R, JavaScript, HTML/CSS, Tcl \\
\textbf{Tools:} Git, NLTK, Jupyter, 
    % Midway, 
    \LaTeX, Pandas, NumPy, Beautiful Soup, Selenium, SciPy, Django, Manim, Jekyll, VMD \\
\textbf{Language:} Native in Mandarin Chinese

\section*{HONORS AND AWARDS}
Uncommon Hacks 2024 --- Winner in the Web Development track. \\ 
Rise Global Challenge --- Finalist. 




\end{document}


